An introduction to pglmm in lme4

### 2019-04-09 vignette.Rmd
almost done?

```{r}
### simulate phylogenetic tree

@@

# Basic parameters
nspp <- 3

@@

```{r}

@@

source("phyloglmm_setup.R")

@@

print(phyZ)

@@

```{r}

source("new_phylo_setup.R")

dat <- (dat %>% mutate(obs = sp))

## everything can be reduce down to formula,data, and a phy object

fitmod <- phylo_lmm2(Y ~ X + (1 |sp) + (1 + X|sp)
			, data=dat 
			, phylonm = "sp" # wishy-washy
			, phyloZ = phyZ # Maybe we just want the phy object and compute this internally
			, nsp = nspp # make default check
			, control=lmerControl(check.nobs.vs.nlev="ignore",check.nobs.vs.nRE="ignore")  ## make default
			, REML = FALSE # make default 
)

>>>>

```{r simdata}
### simulate phylogenetic tree

@@

# Basic parameters
nspp <- 1000

@@

```{r phyloZ}

@@

source("lme4_phylo_setup.R")

@@

# print(phyZ)

@@

```{r fit}

dat2 <- (dat %>% mutate(obs = sp, sp = paste("t",sp,sep="")))

fitmod <- phylo_lmm(Y ~ X + (1 + X|sp)
			, data=dat2
			, phylonm = "sp" 
			, phyloZ = phyZ 
			, control=lmerControl(check.nobs.vs.nlev="ignore",check.nobs.vs.nRE="ignore")  
			, REML = FALSE 
)
